\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\title{Gun Violence Data Reconstruction Report}
\author{Aydin O'Leary and Jack Greenberg }
\date{February 2020}

\begin{document}

\maketitle

\section*{Preliminary Outline [REMOVE THIS WHEN DONE]}

\begin{itemize}
    \item Context: Gun violence in America has been rising over the last 20-ish years. \cite{website:cdc-data}
    \item Big Question: Can we use data reconstruction techniques to predict potential future causes of gun violence and fill in information about past gun violence events?
    \item Small Question: Can we use SVD and PCA techniques to reconstruct data with the reasonable degree of accuracy required to predict potential gun violence events or fill in information about past gun violence events?
    \item We'll use the one hot encoding system \cite{website:wikipedia_one-hot} to represent non-numerical data in numbers (for example, the state in which the gun violence event took place).
    \item We will divide our dataset into two chunks, one for training our algorithm and one for testing it. The training data will consist of the entries from 2013 through 2017, and we will run our tests on data from 2018.
    \item Some other questions about the project space: \begin{itemize}
        \item What is the threshold for accuracy that our algorithm should have?
        \item How anonymized should our reconstructed data be?
        \item What are the implications of predictions that can be made in this space?
        \item Have you seen Minority Report (2002) (predicting future events)?
    \end{itemize}
\end{itemize}

\section*{Summary}
    \begin{itemize}
        \item Includes both big and focused question, and summary of results.
        \item Results will include overall accuracy of the test training data, as well as an example of our algorithm being used
    \end{itemize}
\section*{Introduction}
    \begin{itemize}
        \item Discussion of gun violence in America and uses for an algorithm
        \item Broad description of SVD used in our algorithm
        \item Ethical framework for our algorithm, ways it could go wrong, ways it could be helpful
    \end{itemize}
\section*{Methods}
    \begin{itemize}
        \item Detailed description of SVD with equations
        \item Information about our dataset, how we cleaned the original dataset
        \item Explanation of one-hot encoding for our dataset
    \end{itemize}
\section*{Detailed Findings}
    \begin{itemize}
        \item Results of accuracy of test data
        \item Specific result obtained by feeding algorithm a subset of the training data and having it return the rest of the data for us
    \end{itemize}
\section*{Recommendations}
    \begin{itemize}
        \item Reintroduce ethical context for algorithm and discuss again the ways that it could be used, both for good and bad
    \end{itemize}

\bibliographystyle{plain}
\bibliography{bibliography} 

\end{document}
